Thesis Title

### 2022-03-14 chapters/introduction.tex
finish assembly part

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 2 source/Screenshot 2022-02-25 at 19.11
\caption{\textbf{World Health Organisation Global Priority Pathogens list.} This catalogue includes, besides \textit{Mycobacterium tuberculosis} considered the number one global priority, a list of twelve microorganisms grouped under three priority tiers according to their antimicrobial resistance: critical (\textit{Acinetobacter baumannii}, \textit{Pseudomonas aeruginosa} and \textit{Enterobacteriaceae}), high (\textit{Enterococcus faecium}, \textit{Helicobacter pylori}, \textit{Salmonella} species, \textit{Staphylococcus aureus}, \textit{Campylobacter} species and \textit{Neisseria gonorrhoeae}), and medium (\textit{Streptococcus pneumoniae}, \textit{Haemophilus influenzae} and \textit{Shigella} species). The major objective was to encourage the prioritisation of funding and incentives, align research and development priorities of public health relevance, and garner global coordination in the fight against antimicrobial resistant bacteria. Adapted from \cite{world_health_organization_prioritization_2017}.}
\label{fig:figure2}
\end{figure*}

@@

\subsubsection{Metataxonomics and Operational Taxonomic Units}

@@

@@

>>>>

\mbox{}\\
\vspace{8cm}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 6 source/Figure 2.png}
\caption{\textbf{Principles of current processing of bacterial pathogens.} Schematic representation of the current workflow for processing samples for bacterial pathogens is presented, with high complexity and a typical timescale of a few weeks to a few months. Samples that are likely to be normally sterile are often cultured on rich medium that will support the grown of any culturable organism. Samples contaminated with colonising flora present a challenge for growing the infecting pathogen. Many types of culture media (referred to as selective media) are used to favour the growth of the suspected pathogen.
Once an organism is growing, the likely pathogens are then processed through a complex pathway that has many contingencies to determine species and antimicrobial susceptibility. Broadly, there are two approaches. One approach uses MALDI-TOF for species identification prior to setting up susceptibility testing. The other uses Gram staining followed by biochemical testing to determine species; susceptibility testing is often set up simultaneously with doing biochemical tests. Lastly, depending on the species and perceived likelihood of an outbreak, a small subset of isolates may be chosen for further investigation using a wide range of typing tests. Adapted from \cite{didelot_transforming_2012}}
\label{fig:figure2}
\end{figure*}

@@

\subsubsection{Metataxonomics}

@@

Most second-generation sequencing (see \secref{ssec:2nd_gen_seq} assemblers, such as SPAdes\footnote{\url{https://github.com/ablab/spades/}}, SKESA\footnote{\url{https://github.com/ncbi/SKESA/}} and MEGAHIT\footnote{\url{https://github.com/voutcn/megahit/}}, use a multiple k-mer De Bruijn graph, starting with the lowest size and iteratively adding k-mers of increasing length to connect the graph \citep{bankevich_spades_2012, souvorov_skesa_2018, li_megahit_2015}. Older assemblers, such as Velvet\footnote{\url{https://www.ebi.ac.uk/~zerbino/velvet/}}, Ray\footnote{\url{https://sourceforge.net/projects/denovoassembler/f}} and SoapDeNovo2\footnote{\url{https://sourceforge.net/projects/soapdenovo2/}} use a single k-mer strategy for the De Bruijn graph construction \citep{zerbino_velvet_2008, boisvert_ray_2010, luo_soapdenovo2_2012}.

@@

The success of an assembly is evaluated in two steps: (1) globally, through intrinsic characteristics of the assembly itself, and (2) relative to a reference genome. The computation of the global metrics is performed through statistics inherent to the complete set of contigs assembled per sample, independent of the species/sample of origin. Commonly, these statistics include information on contig number, its median size and number ambiguous bases. The comparison with a reference sequence allows for statistics such as number of misassemblies, meaning contigs that do not reflect the structural organisation in the reference sequence, to be computed.

The assessment and evaluation of genome assemblies has been a relevant field ever since the emergence of the assembly process itself. The most widely adopted is QUAST\footnote{\url{http://quast.sourceforge.net/quast}}, can evaluate assemblies both with a reference genome, as well as without a reference, producing many reports, summary tables and plots to help compare and assess assembly success \citep{gurevich_quast_2013}.
